Project-I by Group MexicoCity

### 2014-11-02 report/paper.tex
01 loss + decideRemove
report update -------------- draft (of final) version available at 20h today --------------------------- comments after 20h -------------------- modifications at 23h --------------------

\end{itemize}

\section{Summary}
In this report, we analyzed a regression dataset and found that ridge regression is a reasonable fit. We estimate that the average test error is 1.213 ($\pm$ 0.02). We tried some feature transformation and found that there is a small improvement giving us a test error of around 1.198 ($\pm$ 0.015). This improvement, however, is not significant.

>>>>

\end{itemize}
These functions are different machine learning methods.

\textcolor{red}{Formula?}

\section{Data observation}
We have two data set. One for regression and one for classification. \begin{description}
\item[Regression] Consists of output variables $\mathbf{y}$ and input variables $\mathbf{X}$. The number of example is $N = 1400$ and each input $\mathbb{x_n}$ has dimensionality $D = 48$. The first $34$ are real valued and the last $14$ are categorical.
\item[Classification]

\end{description}

\section{Data visualization and cleaning}
Most variables seem normally distributed with various means, but the variables 43-48 seem categorical (42 not really normal, looks like the distribution of $y$ actually, 2 Gaussian with different means)
Kstest for normality only confirms that first 33 input variables are indeed random. something fishy about the variables 34-42 that SEEM normal (through histogram distribution)  but are not.\\

The matrix $\tilde{X}$ has rank 36 for regression. That means 13 variables are not correlated to anything (given a threshold of 10 percent of the maximum correlation). Then $\tilde{X}$ is not ill conditioned.
\section{Summary}
In this report, we analyzed a regression dataset and found that ridge regression is a reasonable fit. We estimate that the average test error is 1.213 ($\pm$ 0.02). We tried some feature transformation and found that there is a small improvement giving us a test error of around 1.198 ($\pm$ 0.015). This improvement, however, is not significant.
